---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.


keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

toc               : yes
toc_float         : yes
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : word_document
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Citations in papaja, detele appropriately later

Add the bibtex entry in the .bib file. You can find the entries in Google scholar, 
but double check since it is not always correct. 

Call the citations in the text:

Citation within parentheses	[@R-papaja]

Multiple citations	[@R-papaja; @R-base]

In-text citations	@R-papaja

Year only	[-@R-base]

Only if your citation appears in the text it will also show up in the Reference 
list. Don't manually modify the Reference list.

## Executive Summary 

(150 words) – 0.3 POINTS
Summarize the report. Write this as the very last thing.

What is the main topic you are addressing?

what are your research questions and hypotheses?  

what are your results and the main conclusion?



## Introduction 
(about 1000 words) – 0.5 POINTS
Place your topic of choice within the existing literature and explain what you 
are going to address in this report and why.

*	What is the main topic that is going to be studied in this paper?

*	Why is it important?

*	What are the existing studies that address it already?

*	What are your questions and hypotheses? Why are they important? How are they 
connected to previous work or to a problem you raised?

*	Which methods are you using? Why?

*	How is your work going to contribute to the field/or to whom (e.g., industry)?

*	What does the rest of the report look like? In one short paragraph, list the 
topics of the following sections.

## Methodology

### Dataset 
(about 500 words) 1 POINT (+ BONUS)
*	Which data set are you going to use? Three options:

o	Use readily/easily available data (0 bonus points)

o	Combine two or more existing datasets (max 0.5 bonus points)

o	Scrape or collect your own data (max. 1 bonus point)

*	Clearly explain where the data is coming from:

o	Who collected the data?

o	What is the source?

o	When was the data produced?

o	How was the data collected?

*	Provide descriptive measures of your data (tables, plots, etc.)

*	Why is this data useful to study your topic and answer your research questions?

*	What is the potential bias in the data? How does this affect your results?

### Data analysis (Research Rationale)
(about 500 words) – 1 POINTS
*	Why are these two methods suitable for your data?

*	Why are these two methods suitable for your research questions?

*	Are there other methods to address these questions? If yes, why are the 
methods you chose better for this case?



## Results
(about 2000 words)

### Model 1
(about 1000 words) – 2.5 POINTS

*	Present your results appropriately (plots, tables…) and discuss your findings 
in plain English

*	Discuss the meaning of your findings in relation to your hypothesis. (half of
the points evaluated in this other part)


```{r echo = FALSE, results = 'asis'}
# table example
cn <- c("age", "gender", "eyes_col")
one <- c(7, "M", "BLUE")
two <- c(8, "F", "BROWN")
three <- c(8, "M", "GREEN")
four <- c(7, "F", "PINK")

tab <- rbind(cn, one, two, three, four)
rownames(tab) <- NULL
knitr::kable(tab)
```


### ERGM 
(about 1000) – 2.5 POINTS


* Present your results appropriately (plots, tables…) and discuss your findings 
in plain English

* Discuss the meaning of your findings in relation to your hypothesis. (half of 
the points evaluated in this other part)

Option 1: 

```{r model 1, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(lm.D9))


```

Option 2

```{r model 2, echo = FALSE, results = 'asis'}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(list(lm.D9, lm.D90)))


```


Option 3

```{r model 3, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")


texreg::plotreg(lm.D9)


```


Option 4

```{r model 4, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

texreg::plotreg(list(lm.D9, lm.D90))

```


## Conclusion

(about 350 words) – 0.7 POINTS
What were your topic and research questions again? (1 sentence)

What did you learn from the two analysis you run? *** most important point to 
address 0.5 POINTS here

Who benefits from your findings?

What does remain an open problem?

Can you give suggestions for future work in this area?



\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
