---
title             : "Social Network Analysis in Eurovision Context"
shorttitle        : "SNA Eurovision"
author: 
  - name          : "Krzysztof Wiesniakowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing
affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
toc               : yes
toc_float         : yes
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : word_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Citations in papaja, detele appropriately later

Add the bibtex entry in the .bib file. You can find the entries in
Google scholar, but double check since it is not always correct.

Call the citations in the text:

Citation within parentheses [@R-papaja]

Multiple citations [@R-papaja; @R-base]

In-text citations @R-papaja

Year only [-@R-base]

Only if your citation appears in the text it will also show up in the
Reference list. Don't manually modify the Reference list.

## Executive Summary

(150 words) -- 0.3 POINTS Summarize the report. Write this as the very
last thing.

What is the main topic you are addressing?

what are your research questions and hypotheses?

what are your results and the main conclusion?

## Introduction

The Eurovision Song Contest, which has taken place every year since
1956, is organized by the European Broadcasting Union. It is televised
live throughout Europe and is also broadcast internationally with a
delay. The primary goal of the Eurovision Song Contest is to discover
the most beloved song in Europe. One of the most iconic champions of
this competition is Abba, the Swedish representatives in 1974, who
performed the song "Waterloo." This paper examines the votes cast in the
European song contest in 2023.

Studying social networks within the Eurovision context is of paramount
importance for various reasons. First, it provides invaluable cultural
insights, as Eurovision serves as a reflection of the diverse cultures
and values of participating countries. Additionally, examining voting
patterns illuminates the influence of political and regional alliances
on the integrity of the competition, offering potential avenues for
reform.

Furthermore, the substantial public engagement generated by Eurovision
on social media offers insights into which aspects of the contest
resonate most with the audience. Social network analysis also enables
predictive analytics, aiding contestants, broadcasters, and sponsors in
making informed decisions about the popularity of acts or songs.

Understanding fan communities on social media helps tailor strategies to
engage and mobilize passionate supporters, while assessing marketing and
promotion effectiveness through social networks aids in reaching a
broader audience. Finally, it's crucial for optimizing the digital
experience and gathering audience feedback to enhance the overall
Eurovision experience.

In the field of social networks there has been already done research
regarding voting patterns which as a consequence leads to creating
communities within the Eurovision participants. Dekker A. (2007) [@dekker2007eurovision] has
already conducted the research using Eurovision cast from 2005 where he
analysed the friendship network using techniques previously developed
for valued networks (Dekker, 2005), which combine network-analysis
methods with statistical methods. His analysis revealed a set of
friendship blocs.

In 2019, Angelo S.D. et al. [@D’Angelo_Murphy_Alfò_2019] introduced the concept of modeling
latent spaces in multidimensional networks, specifically focusing on its
application to the exchange of votes within the Eurovision Song Contest.
The model was put into practice to analyze voting patterns in the
Eurovision Song Contest, spanning from 1998 to 2015. This analysis
incorporated cultural and geographical factors. It was discovered that
the only significant factor in explaining observed voting patterns was
the presence of a shared border between two countries. Interestingly,
the similarities among participants during the 1998-2015 period only
partially correlated with their respective geographical locations.

Sentiment analysis has been also used to predict audience voting.
Kumpulainen I. et al.in 2020
@Kumpulainen_Praks_Korhonen_Ni_Rissanen_Vankka_2020 analyzed more than
one million tweets through a variety of techniques, aiming to forecast
the Eurovision Song Contest televoting outcomes. They explored diverse
approaches to sentiment analysis, including English sentiment analysis,
multilingual polarity lexicons, and deep learning. Additionally, they
experimented with translating tweets in the target language to English
to identify the most effective prediction method for the contest.

Thus it can be stated that there is already a social network as well
machine learning research done in regards to Eurovision voting patterns.
Studies take into consideration various aspects but there is lack of
research when it comes to the newest Eurovision editions. Moreover,
there is lack of research when it comes to analyzing the influence of
political system of the country as well as influence of language family.

In this work we will try to answer the following research questions:

RQ1: To what extent countries formulate small communities between each
other in the Eurovision competition?

RQ2: To what extent governmental system influences affects how the
countries distribute their votes during Eurovision competition?

Our research question leads to the following hypothesis:

H0: There is not a significant number of communities within Eurovision
competition. H1: There is a significant number of communities within
Eurovision competition.

H0: Governmental system and language family do not have an influence how
countries distribute their votes Eurovision competition H1: Governmental
system and language family have an effect how countries distribute their
votes during Eurovision competition

Answering aforementioned research questions and hypotheses are going to
help us to understand to certain extent whether there are voting
patterns inside Eurovision as well as to understand what may cause that
phenomenas.

To answer the first research question and to validate the first
hypothesis we are going to run Conditional Uniform Graph test.

This can be achieved by a `sna::cugtest` function that does the graph
generation and computes the network measure. Using a Conditional Uniform
Graph is a valuable approach to assess the number of communities within
a network because it provides a rigorous and controlled framework for
community detection, helps identify meaningful structures, and allows
for statistical analysis and algorithm validation.

To answer the second research question and to validate the second
hypothesis we are going to run Exponential Random Graph Model (ERGM)
test.

In the rest of the report we will carefully describe the datasets which
are going to be used to conduct the research. Data cleaning and if
necessary data preprocessing is going to be run before any
analysis. Descriptive analysis is going to be performed to better
understand the data. Then research rationale is going to be discussed to
provide the reasoning why CUG and ERGM have been chosen as the suitable
models for answering research questions and testing hypotheses.

## Methodology

### Dataset

(about 500 words) 1 POINT (+ BONUS) \* Which data set are you going to
use? Three options:

o Use readily/easily available data (0 bonus points)

o Combine two or more existing datasets (max 0.5 bonus points)

o Scrape or collect your own data (max. 1 bonus point)

-   Clearly explain where the data is coming from:

o Who collected the data?

o What is the source?

o When was the data produced?

o How was the data collected?

-   Provide descriptive measures of your data (tables, plots, etc.)

-   Why is this data useful to study your topic and answer your research
    questions?

-   What is the potential bias in the data? How does this affect your
    results?

### Data analysis (Research Rationale)

(about 500 words) -- 1 POINTS \* Why are these two methods suitable for
your data?

-   Why are these two methods suitable for your research questions?

-   Are there other methods to address these questions? If yes, why are
    the methods you chose better for this case?

## Results

(about 2000 words)

### Model 1

(about 1000 words) -- 2.5 POINTS

-   Present your results appropriately (plots, tables...) and discuss
    your findings in plain English

-   Discuss the meaning of your findings in relation to your hypothesis.
    (half of the points evaluated in this other part)

```{r echo = FALSE, results = 'asis'}
# table example
cn <- c("age", "gender", "eyes_col")
one <- c(7, "M", "BLUE")
two <- c(8, "F", "BROWN")
three <- c(8, "M", "GREEN")
four <- c(7, "F", "PINK")

tab <- rbind(cn, one, two, three, four)
rownames(tab) <- NULL
knitr::kable(tab)
```

### ERGM

(about 1000) -- 2.5 POINTS

-   Present your results appropriately (plots, tables...) and discuss
    your findings in plain English

-   Discuss the meaning of your findings in relation to your hypothesis.
    (half of the points evaluated in this other part)

Option 1:

```{r model 1, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(lm.D9))


```

Option 2

```{r model 2, echo = FALSE, results = 'asis'}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(list(lm.D9, lm.D90)))


```

Option 3

```{r model 3, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")


texreg::plotreg(lm.D9)


```

Option 4

```{r model 4, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

texreg::plotreg(list(lm.D9, lm.D90))

```

## Conclusion

(about 350 words) -- 0.7 POINTS What were your topic and research
questions again? (1 sentence)

What did you learn from the two analysis you run? \*\*\* most important
point to address 0.5 POINTS here

Who benefits from your findings?

What does remain an open problem?

Can you give suggestions for future work in this area?

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
