---
title             : "Social Network Analysis in Eurovision Context"
shorttitle        : "SNA Eurovision"
author: 
  - name          : "Krzysztof Wiesniakowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing
affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
toc               : yes
toc_float         : yes
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : word_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences, include = FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



## Executive Summary

<Still in progress>

## Introduction

The Eurovision Song Contest, which has taken place every year since
1956, is organized by the European Broadcasting Union. It is televised
live throughout Europe and is also broadcast internationally with a
delay. The primary goal of the Eurovision Song Contest is to discover
the most beloved song in Europe. One of the most iconic champions of
this competition is Abba, the Swedish representatives in 1974, who
performed the song "Waterloo." This paper examines the votes cast in the
European song contest in 2023.

Studying social networks within the Eurovision context is of paramount
importance for various reasons. First, it provides invaluable cultural
insights, as Eurovision serves as a reflection of the diverse cultures
and values of participating countries. Additionally, examining voting
patterns illuminates the influence of political and regional alliances
on the integrity of the competition, offering potential avenues for
reform.

Furthermore, the substantial public engagement generated by Eurovision
on social media offers insights into which aspects of the contest
resonate most with the audience. Social network analysis also enables
predictive analytics, aiding contestants, broadcasters, and sponsors in
making informed decisions about the popularity of acts or songs.

Understanding fan communities on social media helps tailor strategies to
engage and mobilize passionate supporters, while assessing marketing and
promotion effectiveness through social networks aids in reaching a
broader audience. Finally, it's crucial for optimizing the digital
experience and gathering audience feedback to enhance the overall
Eurovision experience.

In the field of social networks there has been already done research
regarding voting patterns which as a consequence leads to creating
communities within the Eurovision participants. Dekker A. (2007)
[@dekker2007eurovision] has already conducted the research using
Eurovision cast from 2005 where he analysed the friendship network using
techniques previously developed for valued networks (Dekker, 2005) [@dekker2005] ,
which combine network-analysis methods with statistical methods. His
analysis revealed a set of friendship blocs.

In 2019, Angelo S.D. et al. [@D'Angelo_Murphy_Alfò_2019] introduced the
concept of modeling latent spaces in multidimensional networks,
specifically focusing on its application to the exchange of votes within
the Eurovision Song Contest. The model was put into practice to analyze
voting patterns in the Eurovision Song Contest, spanning from 1998 to
2015. This analysis incorporated cultural and geographical factors. It
was discovered that the only significant factor in explaining observed
voting patterns was the presence of a shared border between two
countries. Interestingly, the similarities among participants during the
1998-2015 period only partially correlated with their respective
geographical locations.

Sentiment analysis has been also used to predict audience voting.
Kumpulainen I. et al.in 2020
@Kumpulainen_Praks_Korhonen_Ni_Rissanen_Vankka_2020 analyzed more than
one million tweets through a variety of techniques, aiming to forecast
the Eurovision Song Contest televoting outcomes. They explored diverse
approaches to sentiment analysis, including English sentiment analysis,
multilingual polarity lexicons, and deep learning. Additionally, they
experimented with translating tweets in the target language to English
to identify the most effective prediction method for the contest.

Thus it can be stated that there is already a social network as well
machine learning research done in regards to Eurovision voting patterns.
Studies take into consideration various aspects but there is lack of
research when it comes to the newest Eurovision editions. Moreover,
there is lack of research when it comes to analyzing the influence of
political system of the country as well as influence of language family.

In this work we will try to answer the following research questions:

RQ1: To what extent countries formulate small communities between each
other in the Eurovision competition?

RQ2: To what extent governmental system influences affects how the
countries distribute their votes during Eurovision competition?

Our research question leads to the following hypothesis:

H0: There is not a significant number of communities within Eurovision
competition. H1: There is a significant number of communities within
Eurovision competition.

H0: Governmental system and language family do not have an influence how
countries distribute their votes Eurovision competition H1: Governmental
system and language family have an effect how countries distribute their
votes during Eurovision competition

Answering aforementioned research questions and hypotheses are going to
help us to understand to certain extent whether there are voting
patterns inside Eurovision as well as to understand what may cause that
phenomenas.

To answer the first research question and to validate the first
hypothesis we are going to run Conditional Uniform Graph test.

This can be achieved by a `sna::cugtest` function that does the graph
generation and computes the network measure. Using a Conditional Uniform
Graph is a valuable approach to assess the number of communities within
a network because it provides a rigorous and controlled framework for
community detection, helps identify meaningful structures, and allows
for statistical analysis and algorithm validation.

To answer the second research question and to validate the second
hypothesis we are going to run Exponential Random Graph Model (ERGM)
test.

In the rest of the report we will carefully describe the datasets which
are going to be used to conduct the research. Data cleaning and if
necessary data preprocessing is going to be run before any analysis.
Descriptive analysis is going to be performed to better understand the
data. Then research rationale is going to be discussed to provide the
reasoning why CUG and ERGM have been chosen as the suitable models for
answering research questions and testing hypotheses.

## Methodology

### Dataset

For this project the data has been collected from several sources [list
of the sources: <https://eurovisionworld.com/eurovision/2023>.]. Using
several sources allowed us to enrich the dataset and run more
comprehensive analysis.

On the eurovision website
[<https://eurovisionworld.com/eurovision/2023>] the data is presented in
a table which by switching the tab on the top of the page can be easily
filtered by Jury or Public votes. Data is presented in a matrix where
columns are created by countries who were giving the points and rows are
represented by countries who were receiving the points. Each entry of
the matrix is represented by the amount of points were given/received.
This data was produced 13th of May 2023 when the final of the tournament
has taken place.

To enrich the data we also collected the information about each
country's language family [the source to language family], country
population [source to country population] and country political system.
This data was manually inserted into csv files which eventually allowed
to transform it to the network object.

As the result, the whole dataset contains of 3 csv files. The first csv
file contains the information about the countries which in this paper
are also going to be referred as nodes, population, country language
family, and country political system. This file is used to create a list
of nodes which is used to create a network object.

The second csv file contains the information about the votes of jurys
from the countries. There are 3 columns in this file sender, receiver
and score which represents the amount of points given from the sender to
receiver. This file is used to create an edge list which is used to
create a first network object.

The third csv file contains the information about the votes from public
from the countries. There are 3 columns in this file sender, receiver
and score which represents the amount of points given from the sender to
receiver. This file is used to create an edge list which is used to
create a second network object.

In this paper 2 networks objects are created and analyzed. The first
network object is created using Node List which comes from the first csv
file and an edge list which represents jurys votes and is created from
the second csv file. The second network object is created using the same
Node List and an edge list which represents public votes and is created
from the third csv file.

The selection of node attributes has been done after doing the research
and discovering research gaps. Furthermore, 3 csv files allowed to
create 2 network objects which as a consequence allows to perform deeper
analysis and reveal potential differences in voting patterns between
jury and public.

#### Potential bias in the dataset

All data is publicly available online in English thus anyone with the
access to the internet can access it. Naturally language barrier can be
a limitation, however, nowadays a lot of online dictionaries are
available to translate the websites immediately. Thus no major biases in
the data have been identified.

<Plots yet to be added>

### Data analysis (Research Rationale)

<still in progress>

## Results

(about 2000 words)

### Model 1

<still in progress>

```{r echo = FALSE, results = 'asis'}
# table example
cn <- c("age", "gender", "eyes_col")
one <- c(7, "M", "BLUE")
two <- c(8, "F", "BROWN")
three <- c(8, "M", "GREEN")
four <- c(7, "F", "PINK")

tab <- rbind(cn, one, two, three, four)
rownames(tab) <- NULL
knitr::kable(tab)
```

### ERGM

<still in progress>

```{r model 1, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(lm.D9))


```

Option 2

```{r model 2, echo = FALSE, results = 'asis'}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

knitr::kable(texreg::matrixreg(list(lm.D9, lm.D90)))


```

Option 3

```{r model 3, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")


texreg::plotreg(lm.D9)


```

Option 4

```{r model 4, echo = FALSE}
# model results display example
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1)

# install.packages("texreg")

texreg::plotreg(list(lm.D9, lm.D90))

```

## Conclusion

<still in progress>

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
\newpage

# Appendix
